---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pRedictwine

<!-- badges: start -->
<!-- badges: end -->

The goal of pRedictwine is to aid in the workflow of a linear regression analysis.
It provides functions that could aid in the steps of loading and tidying the data,
histograms for exploratory analysis, and creating the linear regression model.

Contains 3 functions that are aimed to help in the workflow of a linear regression analysis. Such functions are one to load an online dataset and change the columns' names, another to create appropriate histograms, and a last one to directly create the linear regression model. This package was created mainly for the prediction of wine quality through MLR, found in  https://github.com/DSCI-310-2024/dsci-310_group-7_wine-quality-prediction.

## Installation

You can install the development version of pRedictwine from [GitHub](https://github.com/DSCI-310-2024/pRedictwine) with:

``` r
# install.packages("pRedictwine")
devtools::install_github("DSCI-310-2024/pRedictwine")
```

## Usage

1. Loading a dataset from an URL and changing its column names:
When you want to load an online dataset from an URL and at the same time change the names of the columns, you can do so with load_W_new_col().

```{r}
library(pRedictwine)

dataset_path <- "https://archive.ics.uci.edu/ml/machine-learning-databases/wine-quality/winequality-red.csv"

col_names <- c("fixed_acidity", "volatile_acidity", "citric_acid", "residual_sugar", "chlorides", "free_sulfur_dioxide", "total_sulfur_dioxide", "density", "pH", "sulphates",
 "alcohol", "quality")

delimiter <- ";"

dataset <- load_w_new_col(dataset_path, col_names, delimiter)
```

2. Create a histogram:
If you want to create a histogram with x labels, different coloured values by group, and specifiable x-axis, y-axis, labels; you can do so with create_histogram().

```{r}
library(pRedictwine)

create_histogram(dataset, x = chlorides, group = quality,
                  x_lab = "Chlorides", y_lab = "Count", font_size = 10.5)

```

3. Create a model:
If you want to create a fitted linear regression model, you can do so with fit_linear_reg().

```{r}
library(pRedictwine)

fit_linear_reg(quality ~ ., dataset)

```
